% include the figures path relative to the master file
\graphicspath{ {./content/intro/figures/} }

\section{Introduction}
\label{sec:intro}  % \label{} allows reference to this 

\Ac{cap} has been reported the second most frequently diagnosed cancer of men accounting for 13.6\%~\cite{ferlay2010estimates}. 
In United States, aside from skin cancer, \ac{cap} was considered to be the most commonly diagnosed cancer among men, implying that approximately 1 in 6 men will be diagnosed with \ac{cap} during their lifetime.
The \textit{American cancer society} also reported an estimated 233,000 new cases of prostate cancer in 2014~\cite{CancerFactsFigures2014}. 
To address these dramatic issues, more systematic screenings are organized through \ac{psa} test with further \ac{trus} biopsy if necessary.
However, these tests are unreliable or invasive and that is why further investigations using \ac{mri}-\ac{cad} are motivated. 
In the past decades, several \ac{cad} systems have been proposed in order to assist the radiologists with their diagnosis. 
These systems are usually designed as a sequential process consisting of four stages: pre-processing, segmentation, registration and classification.
As a pre-processing steps, image normalization is an important step of the chain.
Normalization is a highly crucial step to overcome the inter-patient intensity variations occurring, enforce the repeatability, and achieve a robust classification~\cite{Lemaitre2015}.
However, little attention has been dedicated to the problem of normalization of T2W-\ac{mri} prostate images~\cite{Lemaitre2015}.

Artan\,\textit{et al.}~\cite{artan2010prostate,artan2009prostate} and Ozer\,\textit{et al.}~\cite{ozer2009prostate,ozer2010supervised} proposed to normalize the T2W-\ac{mri} images by computing the standard score (i.e., \textit{z-score}) of the \ac{pz} pixels such as: 
\begin{equation}
  I_{s}(x) = \frac{I_{r}(x) - \mu_{PZ}}{\sigma_{PZ}}, \forall x\in PZ ,
  \label{eq:zscore}
\end{equation}
\noindent where, $I_{s}(x)$ and $I_{r}(x)$ are the standardized and the raw signal intensity, respectively, and $\mu_{PZ}$ and $\sigma_{PZ}$ are the mean and standard deviation of the \ac{pz} signal intensity. 
This transformation enforces the image \ac{pdf} to have a zero mean and a unit standard deviation.
However, this normalization is not appropriate if the \ac{pdf} do not follow a Gaussian distribution as illustrated in Fig.\,\ref{fig:fitting}

Lv\,\textit{et al.}~\cite{lv2009computerized} used the method proposed by Nyul\,\textit{et al.}~\cite{nyul2000new}.
For a given patient, a warping function is inferred by matching some specific landmarks (i.e., median and different percentiles) of the current \ac{pdf} to the same landmarks learned during a training phase from several patients. 
The mapping between each landmark is performed using a linear mapping.
Viswanath\,\textit{et al.}~\cite{viswanath2012central} used a variant of the previous method by segmenting first the image using region growing with a pre-defined homogeneity criterion and keeping only the largest region to build the \ac{pdf}.
Nevertheless, the warping functions inferred by these methods can suffer from abrupt changes around the landmarks position, leading to a disrupt \ac{pdf} in the normalized image.  

In this paper, we evaluate and compare different normalization approaches in the context of T2W-\ac{mri} prostate images normalization. Our contribution is threefold: (i) a normalization approach based on a Rician \textit{a priori}; (ii) a normalization approach based on a method used in registration of functional data, without any assumption regarding the \ac{pdf} of the data; (iii) a novel evaluation metric to asses quantitatively the alignment of the \acp{pdf} independently of the assumed distribution. 
These methods will be compared qualitatively and quantitatively, with both \textit{z-score} normalization and piecewise-linear normalization.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master"
%%% End:
